\begin{thebibliography}{00}
    
\bibitem{ref1} Faithfull, M. - SecureTeam (2020). Desktop Application Security Assessment.
\newline
URL: \url{https://bit.ly/3slk7KY}

\bibitem{ref2} Winston W Royce. Managing the development of large software systems. In proceedings of IEEE WESCON, number 8,
pages 328–338. Los Angeles, 1970.
\newline
URL: \url{https://bit.ly/3fBuVRz}

\bibitem{ref3} Ionos - Digital Guide - Waterfall methodology
\newline
URL: \url{https://bit.ly/3mdYudg}

\bibitem{ref4} Atlassian. (2020). Agile project management.
\newline
URL: \url{https://www.atlassian.com/agile/project-management}

\bibitem{ref5} Pahuja, S. (2015, February 15). Scrum for Individuals. InfoQ.
\newline
URL: \url{https://www.infoq.com/news/2015/02/personal-scrum/}

\bibitem{ref6} OpenAPI Specification - Version 3.0.3 | Swagger. (2021). 
\newline
URL: \url{https://swagger.io/specification/}

\bibitem{ref7} Costanza, P., Herzeel, C., \& Verachtert, W. (2019). A comparison of three programming languages for a full-fledged next-generation sequencing tool. BMC Bioinformatics, 20(1), pages 3–5. 
\newline
URL: \url{https://doi.org/10.1186/s12859-019-2903-5}

\bibitem{ref8} Morris, R. (2016, July 28). Rob Pike: Geek of the Week. Simple Talk.
\url{https://bit.ly/3vOGIBb}

\bibitem{ref9} Structs Instead of Classes - OOP in Go. (2020, June 3). Golang Bot.
\newline
URL: \url{https://golangbot.com/structs-instead-of-classes/}

\bibitem{ref10} Stamat, D. (2013, May 12). How We Went from 30 Servers to 2: Go. The Iron.Io Blog.
\newline 
URL: \url{https://blog.iron.io/how-we-went-from-30-servers-to-2/}

\bibitem{ref11} Gorilla Mux - GitHub
\newline
URL: \url{https://github.com/gorilla/mux}

\bibitem{ref12} Gin Gonic Documentation
\newline
URL: \url{https://gin-gonic.com/docs/introduction/}

\bibitem{ref13} Zharova, E. Z. (2021, February 3). The state of Go | The GoLand Blog.
\newline
URL: \url{https://bit.ly/3gWKnZr}

\bibitem{ref14} Angular Tag Trends. (2021). Stack Overflow.
\newline
URL: \url{https://insights.stackoverflow.com/trends?tags=angular}

\bibitem{ref15} Angular Documentation - Router. (2021). Angular. 
\newline
URL: \url{https://angular.io/guide/router}

\bibitem{ref16} Documentation - TypeScript for the New Programmer. (2021). TypeScript Language.
\newline
URL: \url{https://bit.ly/3xR4hel}

\bibitem{ref17} MySQL :: Getting Started with MySQL. (2021).
\newline
URL: \url{https://dev.mysql.com/doc/mysql-getting-started/en/}

\bibitem{ref18} MySQL :: MySQL 8.0 Reference Manual :: 1.2.1 What is MySQL? (2021).
\newline
URL: \url{https://dev.mysql.com/doc/refman/8.0/en/what-is-mysql.html}

\bibitem{ref19} MySQL :: MySQL 5.6 Reference Manual :: 14.2 InnoDB and the ACID Model
\newline
URL: \url{https://dev.mysql.com/doc/refman/5.6/en/mysql-acid.html}

\bibitem{ref20} What is a virtual machine (VM)? (2021). Redhat.
\newline
URL: \url{https://red.ht/2RtyW0x}

\bibitem{ref21} Introduction to Amazon S3 (4:31). (2021). Amazon Web Services, Inc.
\newline
\url{https://aws.amazon.com/s3/}

\bibitem{ref22} Introduction to AWS Elastic Beanstalk. (2021). Amazon Web Services, Inc. 
\newline 
URL: \url{https://aws.amazon.com/elasticbeanstalk/}

\bibitem{ref23} Pedamkar, P. (2021, March 24). Linux vs Windows. EDUCBA.
\newline
URL: \url{https://www.educba.com/linux-vs-windows/}

\bibitem{ref24} What is Docker—Container Registry. (2021). Oracle Ireland.
\newline
URL: \url{https://bit.ly/3aXYnOv}

\bibitem{ref25} Niels Provos and David Mazières - A Future-Adaptable Password Scheme - Proceedings of the FREENIX Track: 1999 USENIX Annual Technical Conference
\newline
URL: \url{https://bit.ly/3xKUfeM}

\end{thebibliography}